\documentclass[11pt]{article}
\usepackage{geometry} % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper} % ... or a4paper or a5paper or ...
%\geometry{landscape} % Activate for for rotated page geometry
\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

\usepackage{graphicx}
\usepackage{amssymb,latexsym} %maths
\usepackage{amsmath,amsfonts,amsthm} %maths
\usepackage{xfrac} %special fractions
\usepackage{paralist} %special listing environmentss
\usepackage{color} %color

\title{Constitution \\
of the\\
University of Alberta\\
Mathematical Sciences Society\\
}
%\date{Amended and Ratified February 9, 2015}
%\date{Amended February 9, 2015}
\author{Revision VIII}

\begin{document}
\maketitle
%\raggedright

\begin{enumerate}[I.]
  \item Name
    \begin{enumerate}[A)]
      \item The organization to which this document pertains shall be known as
        the University of Alberta Mathematical Sciences Society, hereinafter
        referred to as ``the MSS'' or ``the Society.'' The MSS exists under the
        student groups section of the University of Alberta Students' Union
        Constitution.
      \item The symbol of the Mathematical Sciences Society shall be a
        transposed upper case sigma followed by two integral signs to create a
        stylized representation of the Society's initialism.
      \end{enumerate}
  %%%%%%%%%
  \item Mandate

    The MSS has a responsibility to provide the following to its membership:
    \begin{enumerate}[A)]
      \item To organize academic activities designed to improve the knowledge
        and experience of members in the diverse areas of the mathematical
        sciences.
      \item To foster camaraderie by organizing social activities and allow the
        exchange of ideas in an informal atmosphere.
      \item To represent the interest of members before external organizations
        such as the Students' Union.
      \item To maintain the Society lounge in CAB 453.
    \end{enumerate}
  %%%%%%%%%
  \item Membership
    \begin{enumerate}[A)]
      \item Levels of Membership and Eligibility
        \begin{enumerate}[i)]
          \item Associative Membership
            \begin{enumerate}[a)]
              \item Staff, academic or non-academic, and graduate students may
                obtain associate membership at no charge upon request.
            \end{enumerate}
          \item Full Membership
          \begin{enumerate}[a)]
              \item Any undergraduate student, full or part-time, may become a
                full member of the MSS during the academic year in which they
                are registered at the University of Alberta.
              \item The terms ``full member'' and ``voting member'' are
                considered equivalent and may be used interchangeably.
              \item Two thirds of the MSS's total membership must be full
                members.
            \end{enumerate}
        \end{enumerate}
      \item Privileges
        \begin{enumerate}[i)]
          \item Associative Members
            \begin{enumerate}[a)]
              \item Each associate member is entitled to the use of the lounge.
              \item Each associate member is entitled to attend all general
                meetings and Society events, albeit without voting privileges
                or other preferential status.
            \end{enumerate}
          \item Full Members
            \begin{enumerate}[a)]
              \item Each full member is entitled to the use of the lounge.
              \item Each full member is entitled to attend all general meetings
                and Society events.
              \item Each full member may vote at a general meeting.
              \item Each full member is entitled to special discounts on
                certain Society events.
            \end{enumerate}
        \end{enumerate}
      \item Membership Dues
        \begin{enumerate}[i)]
          \item Membership dues must be paid in full before membership is
            granted. This fee of five dollars is non-refundable.
        \end{enumerate}
      \item Terms of Membership
        \begin{enumerate}[i)]
          \item Payment of dues confers membership from the date of payment to
            the beginning of the next academic year.
        \end{enumerate}
      \item Suspension
        \begin{enumerate}[i)]
          \item Any member may have their membership suspended under Article
            III, Section E during a general meeting by a majority vote. Valid
            grounds to suspend membership are violation of the University of
            Alberta Code of Student Behaviour or the MSS's constitution.
        \end{enumerate}
      \item Reinstatement
        \begin{enumerate}[i)]
          \item Any member suspended may have their membership reinstated
            during a general meeting by a two-thirds vote.
        \end{enumerate}
    \end{enumerate}
  %%%%%%%%%
  \item Meetings
    \begin{enumerate}[A)]
      \item General Meeting

      A general meeting may be called by any full member and shall be
        considered valid if and only if all of the following conditions are
        satisfied:
        \begin{enumerate}[i)]
          \item 40\% of the non-executive voting membership must be in
            attendance.
          \item Three members of the executive must be in attendance, one of
            whom must be either the president or the vice-president.
          \item If the secretary is not present, a designate will be appointed
            to take the minutes.
          \item The general meeting must have been advertised at least five
            business days prior to its occurrence.
        \end{enumerate}
      \item Initial General Meeting

      The optional initial general meeting of the MSS in each academic year shall be
        held no more than three weeks after the commencement of the fall
        session. This meeting shall be extensively advertised no less than one
        week prior to its occurrence.

      \item Annual General Meeting

      In February, a special general meeting shall be called for the purpose of
        electing the executive officers. More than 50\% of the total voting
        membership must attend this meeting for the results to be considered
        binding. The newly elected executive will take office on May 1. The
        current executive will make themselves available for operational
        training until that time.

      \item Executive Meetings

      In order for an executive meeting to be considered valid, the following
        conditions must be satisfied.
        \begin{enumerate}[i)]
          \item Quorum must be established; at least three of the executive
            members, including either the president or vice-president, must
            attend.
          \item  If the secretary is not present, a designate will be appointed
            to take the minutes.
        \end{enumerate}
      \item Committee Meetings

      Committee meetings shall be scheduled and conducted at the discretion of
        the committee chair.
      \item Emergency Impeachment Meetings

      Should any full member wish to impeach an executive member, the following
        criteria must be met.
        \begin{enumerate}[i)]
          \item At least two-thirds of the voting membership must meet.
          \item An emergency chair must be nominated and elected by majority
            vote of those present.
          \item The emergency chair must appoint a secretary to record the
            discussion and outcome of the impeachment vote as per Article V,
            Section C.
        \end{enumerate}
      \item Minutes
        \begin{enumerate}[i)]
          \item Full minutes for every MSS meeting, both general and executive,
            must be taken and made available to the membership at large in both
            electronic and printed form no later than one week following the
            meeting.
          \item These minutes must be approved by the next meeting of the body
            which produced them.
        \end{enumerate}
      \item Chairmanship

      Every general and executive meeting will be chaired by the president or,
      in their absence, by the vice-president. In the event of an emergency
      impeachment meeting, this section shall be superseded by Article IV,
      Section F, Subsection ii. Should any conflict arise as to the procedure
      used during a meeting, Robert's Rules of Order shall be considered as the
      definitive source.
      \item Motions

      All motions presented to a general meeting shall be considered passed by
      a majority vote in favour of the motion except as specified by certain
      sections of this document.
    \end{enumerate}
  %%%%%%%%%
  \item Society Executive
    \begin{enumerate}[A)]
      \item Elected Officers (in order of precedence)
        \begin{enumerate}[i)]
          \item President

          It is the responsibility of the President to
            \begin{enumerate}[a)]
              \item Chair all meetings of the MSS when present.
              \item  Oversee the general affairs of the MSS and ensure the
                fulfillment of the Society mandate.
              \item Oversee, in cooperation with the treasurer, the financial
                affairs of the MSS.
              \item Serve as liaison with external groups and individuals.
              \item Represent the interests of the MSS before any external
                organization.
              \item Abstain from voting, except in the event of a tie, where
                the vote of the president shall decide the issue.
              \item Attend mandatory Student Group Services President training.

            \end{enumerate}
          \item Vice President

          It is the responsibility of the Vice President to
            \begin{enumerate}[a)]
              \item Assist the president in all of their responsibilities as
                delegated by the president.
              \item Assume all duties of the president in the event of their
                absence.
              \item Optionally edit, publish, and distribute the society
                newsletter with the assistance of the Newsletter Committee, if
                formed, established under Article VI, Section D, Subsection i.
            \end{enumerate}
          \item Secretary-Treasurer

          It is the responsibility of the Secretary-Treasurer to
            \begin{enumerate}[a)]
              \item Maintain detailed records of all financial transaction
                undertaken by the MSS.
              \item Report the financial status of the Society to the
                membership at all general meetings and upon request.
              \item Oversee the collection of all membership dues and
                generated
                revenues.
              \item Administrate all disbursements of Society funds.
              \item Plan, organize, and oversee the execution of fundraising
                activities with the assistance of the Fundraising Committee,
                if formed, established under Article VI, Section D,
                Subsection ii.
              \item Take minutes at all meetings at which they are present and
                ensure that these minutes are available to the membership as
                per Article IV, Section G.
              \item Assist the executive in the preparation and delivery of
                Society correspondence.
              \item  Keep membership records in order.
              \item Attend mandatory Student Group Services Treasurer
                training.
              \item Make monthly deposits of funds obatined by the Society.
            \end{enumerate}
          \item Social Convenor

          It is the responsibility of the Social Convenor to
            \begin{enumerate}[a)]
              \item Plan and organize social activities with the assistance of
                the Social Planning Committee, if formed, established under
                Article VI, Section D, Subsection iii below.
              \item Provide moral support and assistance to members as
                necessary.
              \item Act as liaison between the Society and the Faculty of
                Science, its various departments, and associated student
                groups as delegated by the president.
            \end{enumerate}
          \item Lounge Officer

          It is the responsibility of the Lounge Officer to
            \begin{enumerate}[a)]
              \item Clean and maintain the Society lounge, CAB 453, with the
                assistance of the Lounge Upkeep Committee, if formed,
                established under Article VI, Section D, Subsection iv below.
              \item Oversee the stocking of the snacks and drinks made
                available for purchase by members in the lounge.
              \item Oversee the availability and state of repair of the
                Society stationary supplies.
              \item Maintain and replace furniture as necessary.
            \end{enumerate}
        \end{enumerate}
        \item Succession

        In the event that any member of the elected executive resigns their
        position or is impeached as per section C below, a temporary
        replacement shall be appointed by the executive until a by-election
        can be held. This election shall be held at the next general meeting
        following the resignation or impeachment. More than 50\% of the total
        membership must be in attendance in order for the results to be
        considered binding.
        \item Impeachment

        Any member of the executive may be impeached in either of the
        following two ways.
          \begin{enumerate}[i)]
            \item Three of the five executive members vote to impeach in
              either
              an executive or general meeting.
            \item A full member calls an emergency impeachment meeting as per
              Article IV, Section F.
          \end{enumerate}
        \item Term of Office

        The term of office of each executive officer shall extend from May 1
        until the following May 1 as per Article IV, Section C.

        \item Past Executive Advisor

        Immediately upon their election, the President shall appoint a
        non-returning member of the previous year's executive to serve in an
        advisory role. In the case of a full returning executive, no advisor
        will be appointed. It is understood that all outgoing executive will
        make their contact information available to incoming executive.

        \item Student Representative for the Department of Mathematical and
          Statistical Sciences Council Meetings

        One member of the MSS must sit on departmental meetings. This memeber
        must be a full member in good standing registered in a program that
        pertains to the Department of Mathematical and Statistical Sciences.
        If the Social Convenor is unavailable for this commitment, another
        executive may fill the role. If all executive are unavailable, the
        executive must elect a general member who fills the requirements to
        sit on the meetings and report back to the executive.
    \end{enumerate}
  %%%%%%%%%
  \item Committees
    \begin{enumerate}[A)]
      \item A committee shall consist of an odd number of voting members,
        chaired by an executive officer. The executive officer shall abstain
        from voting except in the event it is required to break a tie.
      \item Committees are to be formed by the MSS executive for a specific
        task and are responsible only to the executive.
      \item The executive may disband a committee at any time.
      \item Optional Standing Committees

      The following optional standing committees shall meet on a regular basis,
        if formed, during the academic year. The makeup of these committees
        shall be determined by the executive at the Initial General Meeting. At
        their discretion, the executive may remove a member from a standing
        committee, provided that they are replaced at the earliest possible
        opportunity.
        \begin{enumerate}[i)]
          \item Newsletter Committee
            \begin{enumerate}[a)]
              \item The vice-president shall chair the committee.
              \item The committee shall be responsible for editing, publishing,
                and distributing the society newsletter.
            \end{enumerate}
          \item Fundraising Committee
            \begin{enumerate}[a)]
              \item The Secretary-Treasurer shall chair the committee.
              \item The committee shall be responsible for the planning,
                coordination, and execution of fundraising activities.
            \end{enumerate}
          \item Social Planning Committee
            \begin{enumerate}[a)]
              \item The social convenor shall chair the committee.
              \item The committee shall be responsible for the planning and
                organization of social activities.
              \item The committee shall coordinate financial planning and
                revenue collection with the Secretary-Treasurer.
            \end{enumerate}
          \item Lounge Upkeep Committee
            \begin{enumerate}[a)]
              \item The lounge officer shall chair the committee.
              \item  The committee shall be responsible for the cleanliness and
                upkeep of the Society lounge, CAB 453.
            \end{enumerate}
        \end{enumerate}
    \end{enumerate}
  %%%%%%%%%
  \item Elections
    \begin{enumerate}[A)]
      \item Any member is eligible for office if and only if they are a full
        member in good standing. No member may hold more than one elected
        position. All members of the executive must be current undergraduate
        students.
      \item Elections for all executive positions shall be held at the Annual
        General Meeting as defined in Article IV, Section C. Bi-elections are
        held as required in accordance with Article V, Section B.
      \item  Nominations for each executive position will close one day prior
        to the voting for that position. Nominations by either motion or
        volunteer shall be accepted. Nominations must be accepted either in
        person or by signed letter.
        \begin{enumerate}[i)]
          \item Executive positions shall be voted for independently in order
            of precedence as per Article V, Section A.
          \item A deputy returning officer (``DRO'') who is not standing for
            any position shall be appointed by the meeting chair and the final
            decision on all voting will be the right of the DRO.
          \item A scrutineer for each candidate is allowed, provided the
            scrutineer is not the candidate themself.
          \item Voting shall be by secret ballot. Voting by proxy is not
            permitted.
          \item Absentee balloting is allowed under the circmstance that a
            member can not be present at the meeting. Absentee ballots must be
            submitted in a sealed enevlope, signed across the seal, after the
            complete list of nominees has been released and prior to the
            beginning of voting.
          \item Results will be validated by a majority vote. In the case that
            no candidate achieves a majority, the candidate who received the
            least votes, determined by random lot administered by the DRO if
            there is a tie, shall be stricken from the ballot. The position
            shall be voted for again. This procedure shall continue until a
            majority is reached or, if a tie occurs with only two candidates
            remaining, the winner shall be determined by a random lot
            administered by the DRO.
        \end{enumerate}
    \end{enumerate}
  %%%%%%%%%
  \item Financial Administration
    \begin{enumerate}[A)]
      \item Disbursement of Funds
        \begin{enumerate}[i)]
          \item Any disbursement of funds greater than five hundred dollars
            (\$500) must be approved by motion in general meeting.
          \item Any disbursement of funds of five hundred dollars (\$500) or
            less shall be at the discretion of any executive member subject to
            the passing of a subsequent motion at an executive meeting.
          \item Signing authority on any MSS accounts shall be restricted to
            exactly the Secretary-Treasurer and President.
          \item Any member may be reimbursed money, excluding membership dues
            under article III, section C, put towards the operation of the
            Society as approved by the executive.
        \end{enumerate}
      \item Record Keeping and Budget
        \begin{enumerate}[i)]
          \item A detailed ledger of financial affairs shall be maintained by
            the Treasurer and made available to the general membership as per
            article V, Section A, Subsection iii, Paragraphs a and b.
          \item A budget for the school year shall be created and approved by
            the executive team by September 31
          \item The budget shall be updated by the Secretary-Treasurer prior to
            executive meetings throughout the year.
          \item The budget shall be posted online and made available to the
            general membership as per article V, Section A, Subsection iii,
            Paragraphs a and b.
        \end{enumerate}
      \item Audits
        \begin{enumerate}[i)]
          \item The executive shall audit the financial records of the MSS for
            one financial year beginning May 1 and ending April 31 the
            following year. This audit shall occur between the executive
            elections in February and May 1, under the supervision of the
            incoming executive.
          \item Any member may audit the financial records by requesting a
            meeting with the treasurer.
        \end{enumerate}
    \end{enumerate}
  %%%%%%%%%
  \item Amendments and Ratification

    Amendments to this document made by a full member must be submitted in
    writing to the executive and will be immediately tabled for discussion and
    vote at the next general meeting. A two-thirds majority vote is necessary
    to approve a constitutional amendment. The constitution will be reviewed
    once every two years and ratified if needed. The Secretary-Treasurer will
    maintain documentation of review periods when the constitution is reviewed
    but not ratified.
  %%%%%%%%%
  \item Disbandment
    \begin{enumerate}[A)]
      \item The Mathematical Sciences Society may be disbanded by a unanimous
        vote of the entire voting membership at a general meeting.
      \item  In the event of disbandment, all funds shall revert to the
        Department of Mathematical and Statistical Sciences, University of
        Alberta.
    \end{enumerate}
\end{enumerate}

These amendments ratified March 3, 2017 \  by:

Jesse Frohlich, President\\
Allison Roth, Vice President\\
Fatima Davelouis Gallardo, Secretary-Treasurer\\
Sarah Hunt, Social Convenor\\
Colin A'Hearn, Lounge Officer

\end{document}
